Molecular alignment at graphene surface determines tansport properties of graphene transistors

### 2020-04-03 manuscript.tex
Update manuscript.tex
first reading

  Graphene field-effect transistor structures were used to investigate the role of molecular alignment on charge transport properties of heterostructures comprising a single-layer graphene and variable thickness of N,N'-bis(n-octyl)-(1,7\&1,6)-dicyanoperylene-3,4:9,10-bisdicarboximide (PDI8-CN2) - an n-type organic semiconductor. Our atomic force microscopy data show that under selected growth conditions PDI8-CN2 grows in a layer-by-layer fashion up to a second monolayer. The firs layer comprises flat-lying molecules, whereas the molecules in the second layer orient themselves in an upright orientation. Transconductance measurements show that the flat-lying molecules have little effect on the position of the Fermi level in graphene. Upright oriented molecules in the second layer instead have a strong effect as to neutralize native $p$-type doping of graphene and cause a shift of charge-neutrality level towards the Dirac point. We interpret such behavior in terms of different orientation of the surface dipole on layers with different molecular orientations. At the same time the overall mobility of the charge carriers reaches values exceeding 3000 cm$^{2}$/Vs. We 
\end{abstract}

@@

OS growth on graphene is characterized by...

@@

The understanding of morphological properties of the OS layer and its growth mode is important for the interpretation of the charge transport data presented in the following.  In organic semiconductors charge transport proceeds by hopping in a manifold of localized molecular electronic states and is thus strongly dependent on the relative orientation of the molecules and the degree of positional disorder in the layers.  On graphene instead, charge transport is characterized by Bloch-like extended states, which reside, in the case of a single-layer graphene in a relatively disorder-free environment.  The effect of PDI8-CN2 layers on charge transport through graphene was studied by measuring the transfer characteristics of GFETs with different amounts of PDIF8-CN2 grown on graphene channel. Typical evolution of resistance for clean graphene and  two different coverages is illustrated in Figure \ref{fig:3}, where we show transfer the results of measurements (symbols) obtained on GFETs comprising clean single-layer (red curve), GFET with PDI8-CN2 coverage of 1 minute and PDI8-CN2 (blue curve) and with coverage of 3 minutes (green curve).  Only a forward gate sweep (from $V_g<0$ to $V_g>0$) data are shown. A minimal hysteresis was observed (See Supplementary information) indicating low density of traps that would originate from the structural and/or chemical defects in the layers. Also shown are the results of fitting to a model function (black solid curves) explained below.

@@

We observe transfer characteristics of GFET comprising clean graphene exhibiting charge-neutrality point at back-gate voltage of 8.5 V.  The position of CNP relative to the Dirac point (0 V) is consistent with p-type doping of graphene caused by the trap states on SiO$_{2}$ surface and chemical redox reaction occurring at the graphene/SiO$_{2}$ interface\cite{feng-2014,peng-2017,lafkioti-2010}.  In addition to the shift of the conductivity minimum we observe also a strong reduction in the slope of the transfer curve occurring at about 3.6 V, leading to a plateau of the drain current.  Such behavior is commonly present in GFETs with relatively short channels, where the role of the metallic contacts becomes important\cite{bartolomeo-2015,nouchi-2008,nouchi-2014}. Two principal mechanisms in GFET affect charge transport under ambient conditions. First is already mentioned doping of the channel with airborne species. The second is related to the graphene doping under metallic contacts\cite{farmer-2009,giovannetti-2008,lee-2008,mueller-2009}.  Several groups report the evidence that metallic contacts induce doping of the underlying graphene \cite{giovannetti-2008,mueller-2009,huard-2008}, and the amount of transferred charge depends on the difference of metallic work function and the work function of graphene.  Specifically, Au contacts used in our experiments cause p-type doping, according to the work by Giovanetti et al.\cite{giovannetti-2008}, causing a shift in Fermi level of 0.3 eV in the direction away from the vacuum level, across the Dirac point. In addition, changes in the interface charge density may be a consequence of Fermi-level depinning at the metal/graphene interface and is related to microscopic interface environment that is characterized by interdiffusion of metallic atoms and/or oxide interlayer\cite{nouchi-2008,nouchi-2014}. Since Fermi level at such interfaces is not pinned or only partially pinned\cite{dibartolomeo-2011}, the interface charge density may be affected by the applied gate voltage, which is not the case for the abrupt interfaces.  In the channel instead, we can calculate the position of the Fermi level relative to the Dirac point in graphene ($\Delta E$) from the measured position of CNP (Figure \ref{fig:3}), using the approach from Ref. \onlinecite{wang-2008}:
\begin{equation}
  \label{eq:1}
  \Delta E = \hbar v_{F}\sqrt{\pi\alpha|V_{g}-V_{D}}
\end{equation}

where $v_F=0.8\times10^6$ m/s, and $\alpha=7.2\times10^{14}$ cm$^{-2}$ V$^{-1}$. For the value $|V_g-V_D |=8.5$ V we obtain the position of the Fermi level to be 0.073 eV below the Dirac point. The channel structure can therefore be regarded as $p^{++}/p/p^{++}$. A consequence of such variation of charge density within the structure are deviations from the linear transfer lineshapes, which in extreme cases may result in curves may extreme with double dips\cite{nouchi-2014,nam-2012}, or in less extreme exhibiting an abrupt change in slope continuing to a plateau.

\subsection{Transconductance - 1st coverage}
\label{sec:first}

@@

\subsection{Transconductance of the complete PDIF9 layer}
\label{sec:complete}

@@

The resistance plots calculated from the data used to plot Figure \ref{fig:4}.  Are shown in modeled the transfer characteristics were modeled under the following assumptions. The gate voltage is a sum of contributions due to the quantum capacitance, given by the position of the Fermi level  ($E_F$) in graphene and the  electrostatic potential difference between the graphene layer and the gate contact, given by $n\cdot e/C_{ox}$ with $C_{ox}$ capacitance of the gate dielectric and $n$  charge carrier concentration\cite{sze-2006}[26].  However, the gate capacitance $C_{ox}=(\epsilon_0\epsilon)/d_{ox} =1.2\times10^8$ F cm$^{-2}$, with dielectric constant of SiO$_{2}$  $\epsilon \approx 4$ and $d_{ox}=$300 nm.  Considering the typical charge carrier densities on the order of $10^{13}$ cm$^{-2}$ the potential difference accommodated by the bottom gate contact amounts ot 100 V, which is considerably larger than the Fermi level shift in graphene.  Quantum capacitance in the case of bottom gate contact may therefore be safely neglected\cite{das-2008}. The drain current was  calculated as:
\begin{equation}
  \label{eq:2}
  I_{D}=\frac{W}{L}\mu n e)V_{D}- 2I_{D}R_{C}
\end{equation}

>>>>

  Graphene field-effect transistor structures were used to investigate the role of molecular alignment on charge transport properties of heterostructures comprising a single-layer graphene and variable thickness of N,N'-bis(n-octyl)-(1,7\&1,6)-dicyanoperylene-3,4:9,10-bisdicarboximide (PDI8-CN2) - an n-type organic semiconductor. Our atomic force microscopy data show that under selected growth conditions PDI8-CN2 grows in a layer-by-layer fashion up to a second monolayer. The first layer comprises flat-lying molecules, whereas the molecules in the second layer orient themselves in an upright orientation. Transconductance measurements show that the flat-lying molecules have little effect on the position of the Fermi level in graphene. Upright oriented molecules in the second layer instead have a strong effect as to neutralize native $p$-type doping of graphene and cause a shift of charge-neutrality level towards the Dirac point. We interpret such behavior in terms of different orientation of the surface dipole on layers with different molecular orientations. At the same time the overall mobility of the charge carriers reaches values exceeding 3000 cm$^{2}$/Vs. We 
\end{abstract}

@@

OS growth on graphene is characterized by... expansd on this and add some refs

@@

The understanding of morphological properties of the OS layer and its growth mode is important for the interpretation of the charge transport data presented in the following.  In organic semiconductors charge transport proceeds by hopping in a manifold of localized molecular electronic states and is thus strongly dependent on the relative orientation of the molecules and the degree of positional disorder in the layers.  On graphene instead, charge transport is characterized by Bloch-like extended states, which reside, in the case of a single-layer graphene in a relatively disorder-free environment.  The effect of PDI8-CN2 layers on charge transport through graphene was studied by measuring the transfer characteristics of GFETs with different amounts of PDIF8-CN2 grown on graphene channel. Typical evolution of transconductance current for clean graphene and  two different coverages is illustrated in Figure \ref{fig:3}, where we show the results of measurements (symbols) obtained on GFETs comprising clean single-layer (red curve), GFET with PDI8-CN2 coverage of 1 minute and PDI8-CN2 (blue curve) and with coverage of 3 minutes (green curve).  Only a forward gate sweep (from $V_g<0$ to $V_g>0$) data are shown. A minimal hysteresis was observed (See Supplementary information) indicating the density of shallow traps is less than \textbf{XX cm$^{-2}$ - we can calculate this from the dirac shift due to hysteresis}

@@

We observe transfer characteristics of GFET comprising clean graphene exhibiting charge-neutrality point at back-gate voltage of 8.5 V.  The position of CNP relative to the Dirac point (0 V) is consistent with p-type doping of graphene caused by the trap states on SiO$_{2}$ surface and chemical redox reaction occurring at the graphene/SiO$_{2}$ interface\cite{feng-2014,peng-2017,lafkioti-2010}. 
\textbf{Here it is not clear to WHAT we compare.}   
In addition to the shift of the conductivity minimum we observe also a strong reduction in the slope of the transfer curve occurring at about 3.6 V, leading to a plateau of the drain current.  Such behavior is commonly present in GFETs with relatively short channels, where the role of the metallic contacts becomes important\cite{bartolomeo-2015,nouchi-2008,nouchi-2014}. Two principal mechanisms in GFET affect charge transport under ambient conditions. First is already mentioned doping of the channel with airborne species. The second is related to the graphene doping under metallic contacts\cite{farmer-2009,giovannetti-2008,lee-2008,mueller-2009}.  Several groups report the evidence that metallic contacts induce doping of the underlying graphene \cite{giovannetti-2008,mueller-2009,huard-2008}, and the amount of transferred charge depends on the difference of metallic work function and the work function of graphene.  Specifically, Au contacts used in our experiments cause p-type doping, according to the work by Giovanetti et al.\cite{giovannetti-2008}, causing a shift in Fermi level of 0.3 eV in the direction away from the vacuum level, across the Dirac point. In addition, changes in the interface charge density may be a consequence of Fermi-level depinning at the metal/graphene interface and is related to microscopic interface environment that is characterized by interdiffusion of metallic atoms and/or oxide interlayer\cite{nouchi-2008,nouchi-2014}. Since Fermi level at such interfaces is not pinned or only partially pinned\cite{dibartolomeo-2011}, the interface charge density may be affected by the applied gate voltage, which is not the case for the abrupt interfaces.  In the channel instead, we can calculate the position of the Fermi level relative to the Dirac point in graphene ($\Delta E$) from the measured position of CNP (Figure \ref{fig:3}), using the approach from Ref. \onlinecite{wang-2008}:
\begin{equation}
  \label{eq:1}
  \Delta E = \hbar v_{F}\sqrt{\pi\alpha|V_{g}-V_{D}|}
\end{equation}

where $v_F=0.8\times10^6$ m/s, and $\alpha=7.2\times10^{14}$ cm$^{-2}$ V$^{-1}$. For the value $|V_g-V_D |=8.5$ V we obtain the position of the Fermi level to be 0.073 eV below the Dirac point. The channel structure can therefore be regarded as $p^{++}/p/p^{++}$. A consequence of such variation of charge density within the structure are deviations from the linear transfer lineshapes, which in extreme cases TODO: may result in curves may extreme with double dips\cite{nouchi-2014,nam-2012}, or in less extreme exhibiting an abrupt change in slope continuing to a plateau.

\subsection{Transconductance - submonolayer coverage}
\label{sec:first}

@@

\subsection{Transconductance of the complete PDIF8-CN2 layer}
\label{sec:complete}

@@

The resistance plots $R=I_{DS}/V_{G}$ from the transconductivity are presented in Figure \ref{fig:4}. The transfer characteristics were modeled under the following assumptions. The gate voltage is a sum of contributions due to the quantum capacitance, given by the position of the Fermi level  ($E_F$) in graphene and the  electrostatic potential difference between the graphene layer and the gate contact, given by $n\cdot e/C_{ox}$ with $C_{ox}$ capacitance of the gate dielectric and $n$  charge carrier concentration\cite{sze-2006}[26].  The dielectric capacitance is $C_{ox}=(\epsilon_0\epsilon)/d_{ox} =1.2\times10^8$ F cm$^{-2}$, with the dielectric constant of SiO$_{2}$  $\epsilon \approx 4$ and $d_{ox}=$300 nm.  Considering the typical charge carrier densities on the order of $10^{13}$ cm$^{-2}$ the potential difference accommodated by the bottom gate contact amounts to 100 V, which is considerably larger than the Fermi level shift in graphene.  Quantum capacitance in the case of bottom gate contact may therefore be safely neglected\cite{das-2008}. The drain current was modeled as:
\begin{equation}
  \label{eq:2}
  I_{D}=\frac{W}{L}\mu n e)V_{D}- 2I_{D}R_{C}
\end{equation}
